Product graphics

### 2009-12-01 product-graphics.tex
Note about conditional densities
Better equal bin size example

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{part-fluct}%
    \includegraphics[width=0.5\linewidth]{part-fluct-cond}
  \caption{Distribution of age (in decades) and marital status.  All combinations of the two variables are present.}
  \label{fig:fluct}
\end{figure}

@@

>>>>

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{part-fluct}%
    \includegraphics[width=0.5\linewidth]{part-fluct-cond}
  \caption{(Left) Distribution of age (in decades) and marital status.  All combinations of the two variables are present. (Right) Distribution of health status and year of survey. Health status was not recorded for three years.}
  \label{fig:fluct}
\end{figure}

@@

An alternative approach is use density estimates (or conditional density estimates) and plot with continuous area plots.  As in: Hofmann, H., Theus, M. (2005), Interactive graphics for visualizing conditional distributions, Unpublished Manuscript.
